\chapter{Experiment}

In the Experiment an austrian one cent coin was examined. The goal of the experiment is to understand the principle of the OCT and get to know the usage of the system.

\section{Start-up of the OCT system}

To start the OCT-system first the measurement computer, the scanning mirror drivers, the detector unit and the Laser has to be switched on. The laser is operational if the LED labled 'ready' is on. At the measurement computer the LabView program 'OCT\_student.vi' is started.

To check the functionality of the system a 'continous scan' is performed. The current plots of the A-scan in k-space and z-space are shown in the LabView window. In the A-scan in z-space a peak is visible. This represents the position of the surface of the sample. The position of the sample can be moved by a positioning screw. If the position of the peak is moved below zero, another peak becomes visible moving in positive direction. Thus the modulation of the A-scan in k-space consists of two symetrical peaks in z-space. Since k-space and z-space are related by a fourier transform (cf. \ref{sec:fourier}), the modulation carrying the information must be sinusodial. \comseb{versteht man das?}
With this setup only the difference of the optical path lenght of the reference and the sample arm is measured. So when moving the peak below zero, another peak becomes visible moving in positive direction. 
\comwo{ist es nicht so?}
When turning on the positioning screw and moving the sample, the amplitude of the peak in z-space changes. This is because of the lens that focuses the beam on the sample. The maximum peak amplitude is when the beam is focused. By moving the sample out of the focus the amplitude gets smaller.

As another check, the optical path was one time blocked at the sample side and one time at the reference side. If this is done, in both ways the peak in z-domain vanishes, because there is no more interference. Though the A-scans in z-domain differ significantly. 
If the reference path is blocked, only the back scattered light of the sample hits the detector. Thus the intensity of the detected signal is orders of magnitude higher in the case of a blocked sample path.


\section{Performing a 3D-scan of the sample}

In the next step a 3D scan of an Austrian one cent coin was recorded. The sample was mounted in the OCT-System by the advisor of the experiment in advance. The scan was first performed with an angle between -10° to 1° in x-direction and an angle of -7° to 7° in y-direction. The stepsize was choosen as 1° for a first try. The obtained measurement data were analyzed be the MATLAB script 'OKT\_OCT\_3D.m'. \todo{jetzt beschreiben was das script macht}